\chapter{Conclusion}
\label{cha:conclusion}

\textit{"The goal of Semantic Web research is to transform the Web from a linked document repository into a distributed knowledge base and application platform, thus allowing the vast range of available information and services to be more effectively exploited."}
\begin{flushright} Ian Horrocks \cite{HorSSF} \end{flushright}

\noindent According to Handbook of Knowledge Representation \cite{HLP08}, \textit{"OWL has become the most used KR language in the history of the field, not because of its particular representational power, but rather because it was designed to be a common syntax usable by many KR systems, to be webized for easier sharing of ontologies and concepts, and to be expressive enough for many problems without totally sacrificing scalability"}.

Increasingly number of tools designed for OWL is both cause and motivation for the community, to develop ontologies in many various fields, not only in the scope of Semantic Web. There are areas like: biology, medicine, geography, geology, astronomy, agriculture or defense, in which ontologies are becoming adopted \cite{HLP08}.

Modern ontology development tools such as Protégé allow users to maintenance and built ontologies in quick, efficient way. They provide intelligent guidance to find mistakes similar to a debugger in a programming environment because of description logics reasoners support. That is also the reason, why Protégé is ideal as a rapid prototyping environment in which ontology designers can instantly create individuals of specific classes in their ontology and experiment with semantic restrictions \cite{OntDrivDev}.

Development of Semantic Web applications with the support of recent powerful tools is quite inspiring development task. Ontology-driven development with the support of agile methodologies is very efficient implementation process. Ontologies can be developed directly by domain experts. Because of direct access to executable systems, charged by recently developed domain models, feedbacks can be made frequently. Best practices from agile methodologies, effective at delivering a particular outcome, can be used in development high-quality domain models. Domain experts may work together with programmers, which can guarantee coherent testing and fast implementation processes.
